%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {PM/QA} % Job title
    {Web Design Café} % Organization
    {Adelaide, Australia} % Location
    {Sep. 2021 - present} % Date(s)
    {
      \begin{cvitems} 
      \item {Developing web pages for the clients}
      \item {Customising CSS of WordPress themes}
      \item {Setting up WordPress plugins}
      \item {Communication with the clients}
      \item {Organisation and coordination of the team}
      \end{cvitems}
    }




%---------------------------------------------------------
  \cventry
    {Full Stack Software Developer} % Job title
    {General Assembly} % Organization
    {Australia} % Location
    {Nov. 2020 - Aug. 2021} % Date(s)
    {
    {
    During the course I have built a number of projects using different technologies stacks. The most mature of them is Resume Builder App - The open-source web application for fast and easy creation and publishing (with unique public URL) of resumes 'tailored' for each particular vacancy.
    }
    \begin{cvparagraph}
    \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textcolor{awesome}{\href{https://github.com/olimstv/resume-builder-app}{lets.Get(IT)}} - built using React, Next.js, MongoDB. Building this application, I've learned that integration of different technologies into one app might be challenging, but also it gives a significant improvement of developer's skills and knowledge base}
        \item {\textcolor{awesome}{\href{https://github.com/olimstv/rails_notes_app}{Memo}} - a simple notes-gathering app, built with React and Ruby on Rails, using PostgreSQL database. Learning how to build a backend using Ruby on Rails has broadened my perspective as a developer}
        \item {\textcolor{awesome}{\href{https://github.com/olimstv/countless_app_v2.0}{CountLess}} - a budget app that helps track incomes and spending. Main focus for this project was building backend. I learned how to protect routes, how to use Passport.js package and  a basics of SSR using Handlebars}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {} % Job title
    {Relocation} % Organization
    {Australia} % Location
    {Feb. 2019 - Nov. 2020} % Date(s)
    {
    {During this period (after moving to Australia), I put all my efforts into settling on the new place, learned a new culture, and embraced a commitment towards change and personal development. I continued my self-education in Software Development until I decided to take a leap and enrolled in a Full Stack Software Engineering Immersive course of General Assembly}
    \begin{cvparagraph}
    \end{cvparagraph}
    }



%---------------------------------------------------------
  \cventry
    {Software Automation Test Engineer} % Job title
    {GlobalLogic} % Organization
    {Lviv, Ukraine} % Location
    {Nov. 2017 - Feb. 2019 and Sep. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{
    Testing software for a medical device (insulin pump), utilizing a custom set of frameworks and libraries, using JavaScript language.
    }
        \item {Writing test scripts and test scenarios to meet acceptance criteria and quality standards}
        \item {Performing formal testing to provide the results for the Federal Drug Administration (FDA)}
        \item {Automated test code-review and test stabilization}
        \item {Reviewing design inputs according to the scope of testing issues}
        \item {Creation and updating of UI and Functional Test Cases (manual and automation)}
        \item {System components and functions analysis}
        \item {Performing iteration analysis and test planning}
        \item {Participation in knowledge-sharing activities}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Assurance Test Engineer} % Job title
    {Rolique} % Organization
    {Lviv, Ukraine} % Location
    {Jul. 2017 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} 
      \item{Testing of a CRM web application for the “INTERMATE Media GmbH".}
        \item {Manual testing of the developing features and regression testing, writing product, and test documentation}
        \item {Analyzing client requests for validity and feasibility}
        \item {Documenting results of test execution and bug reporting}
        \item {Performing fortnightly demos for presentation to the product owners}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Testing Automation Engineer} % Job title
    {QALight} % Organization
    {Kyiv, Ukraine} % Location
    {jun. 2014 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      {
      Testing a Social Event Discovery Platform – a web-based platform that delivers content and information on entertainment and business events within Europe.
      }
      \item {Primary responsibilities: manual testing of the developing features and regression testing.}
        \item {Analyzed business requirements and suggested improvements to the product features}
        \item {Developed test cases for functional and regression testing of the project Actify}
        \item {Validated application’s GUI for compliance with Usability guidelines published by US Department of Human Services}
      \end{cvitems}
    }




\end{cventries}
